Status Nov. 2018

### 2018-11-26 r/Status Nov. 2018.Rmd
11/26 more

### Site-level data
```{r, echo=F, message=F, warning=F}
gamm_s <- gamm(fr_mean ~ species_code + phase + s(length_m) + s(pc1_bent) + s(pc2_bent) + s(scar_bm), 
           family = gaussian(link=identity),
           random = list(island=~1),
           method = "REML",
           data = sum_ssp_pca
           )
summary(gamm_s$gam)
plot(gamm_s$gam,pages=1)
plot(gamm_s$lme) # not too heteroskedastic?
AIC(gamm_s$lme)

# Confirming low VIF among predictor variables with site-level model
vif(lme(fr_mean ~ phase + length_m + scar_bm + pc1_bent + pc2_bent, 
        data = sum_ssp_pca,
        random = ~1 | island, 
        na.action = na.omit
        )) # all <3
```

### Individual-level data
```{r}
gamm_id <- gamm(fr ~ species_code + phase + s(length_cm) + s(pc1_bent) + s(pc2_bent) + s(scar_bm) 
              # +
              #   s(length_cm, by = as.numeric(species_code == "qup")) +
              #   s(pc1_bent, by = as.numeric(species_code == "qup")) +
              #   s(scar_bm, by = as.numeric(species_code == "qup"))
              , 
           family = gaussian(link=identity),
           random = list(island=~1),
           method = "REML",
           weights = varIdent(form =~ 1 | species),
           data = sum_id_pca
           )
summary(gamm_id$gam)
plot(gamm_id$gam,pages=1)
plot(gamm_id$lme) # shows some heteroskedasticity
AIC(gamm_id$lme)

# Confirming low VIF among predictor variables with site-level model
vif(lme(fr ~ species + phase + length_cm + scar_bm + pc1_bent + pc2_bent, 
        data = sum_id_pca,
        random = ~1 | island, 
        na.action = na.omit
        )) # prints strange when include RBP data
```

## SEM results

>>>>

### Site-level data
```{r, echo=F, message=F, warning=F}
gamm_s <- gamm(fr_mean ~ species_code + phase + s(length_m) + s(pc1_bent) + s(pc2_bent) + s(scar_bm), 
           family = gaussian(link=identity),
           random = list(island=~1),
           method = "REML",
           data = sum_ssp_pca
           )
summary(gamm_s$gam)
plot(gamm_s$gam,pages=1)
plot(gamm_s$lme) # not too heteroskedastic?

```

Confirming low VIF among predictor variables with site-level model
```{r, echo=F, message=F, warning=F}
vif(lme(fr_mean ~ phase + length_m + scar_bm + pc1_bent + pc2_bent, 
        data = sum_ssp_pca,
        random = ~1 | island, 
        na.action = na.omit
        )) # all <3
```

### Individual-level data
```{r, warning=F, message=F, echo=F}
gamm_id <- gamm(fr ~ species_code + phase + s(length_cm) + s(pc1_bent) + s(pc2_bent) + s(scar_bm) 
              # +
              #   s(length_cm, by = as.numeric(species_code == "qup")) +
              #   s(pc1_bent, by = as.numeric(species_code == "qup")) +
              #   s(scar_bm, by = as.numeric(species_code == "qup"))
              , 
           family = gaussian(link=identity),
           random = list(island=~1),
           method = "REML",
           weights = varIdent(form =~ 1 | species),
           data = sum_id_pca
           )
summary(gamm_id$gam)
plot(gamm_id$gam,pages=1)
plot(gamm_id$lme) # shows some heteroskedasticity
```

Confirming low VIF among predictor variables with id-level model
```{r, warning=F, message=F, echo=F}
vif(lme(fr ~ species + phase + length_cm + scar_bm + pc1_bent + pc2_bent, 
        data = sum_id_pca,
        random = ~1 | island, 
        na.action = na.omit
        )) # prints strange when include RBP data
```

## SEM results?

```{r, echo=F, message=F, warning=F}
knitr::include_graphics(here("figs/sem.png"))
```

Notes: Still troubleshooting getting full SEM to run, unsure about how to deal with different data layers/sample sizes. If aggregating to the site level, I will be limited in the number of variables I can include (~8), though I could run separate models by species/phase. I could also use piecewise SEM (e.g. Miller et al. 2018), though does not allow for latent variables.
